### 2021-12-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@2305e0d8834b4252a839573bb30ef9fe5525ff75 🚀

Informedness (\textbf{Youden1950IndRat?}) (also known as bookmaker
informedness or the True Skill Statistic) is
\(\text{TPR}+\text{TNR}-1\), where \(\text{TPR}= tp/(tp+fn)\) and
\(\text{TNR} = tn/(tn+fp)\); informedness can be used to find the
optimal cutpoint in thresholding analyses (Schisterman et al., 2005).
The MCC is defined as

@@

>>>>

Informedness (Youden, 1950) (also known as bookmaker informedness or the
True Skill Statistic) is \(\text{TPR}+\text{TNR}-1\), where
\(\text{TPR}= tp/(tp+fn)\) and \(\text{TNR} = tn/(tn+fp)\); informedness
can be used to find the optimal cutpoint in thresholding analyses
(Schisterman et al., 2005). The MCC is defined as

@@

\leavevmode\hypertarget{ref-Youden1950IndRat}{}%
Youden, W. J. (1950). Index for rating diagnostic tests. \emph{Cancer},
\emph{3}(1), 32--35.
\url{https://doi.org/10.1002/1097-0142(1950)3:1\%3C32::AID-CNCR2820030106\%3E3.0.CO;2-3}
